### 2014-09-11 A1/writeup/writeup.tex
small change

Finally, we recognize that our metric of uniqueness could be improved upon. For instance, it would be interesting to include bigram features in our vector space review representation. Also, our consideration is limited to extremely simple lexical review features only. A more complete analysis, for instance, might include a subset of the dozens of more complex potential review features used by Ghose and Ipeirotis \cite{ghose2011estimating}. Our analysis also doesn't control for reviewer characteristics, which, given the complex social structure potentially underlying review sites like Amazon, is a potential avenue for future exploration.

>>>>

Finally, we recognize that our metric of uniqueness could be improved upon. For instance, it would be interesting to include bigram features in our vector space review representation. Also, our consideration is limited to extremely simple lexical review features only. A more complete analysis might include a subset of the dozens of more complex potential review features used by Ghose and Ipeirotis \cite{ghose2011estimating}. Our analysis also doesn't control for reviewer characteristics, which, given the complex social structure potentially underlying review sites like Amazon, is a potential avenue for future exploration.
